demographicvariablesregression

### 2023-02-15 combined data set/demovariablesregression.Rmd
wilcoxon rank sum test on caste and urban_rural

summary(joineddf)

@@

summary(demovars)
table(demovars$gender)

@@

p1 <- sum_gender%>% 
  filter(Technology %in% c("Wind","Nuclear","Solar","Oil","Hydro","Gas","Coal")) %>%
  ggplot(aes(x=Technology, y= mean, fill = gender))+
  geom_bar(stat="identity", position=position_dodge())+
  #geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=0.2, position=position_dodge(0.9)) +
  ylim(0,5)+
  scale_fill_manual(values=c("red", "blue"), name="legend")+
  labs(y = "Mean perceivd risk", x = "Energy Technologies")+
  ggtitle("Perceived risk and benefit from centrally owned energy technologies by gender")+
  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))

p2 <- sum_gender%>% 
  filter(Technology %in% c("INDHydro", "INDSolar", "INDWind", "INDBiogas","INDDiesel", "INDKerosene","INDFirewoodetc","INDLPG")) %>%
  ggplot(aes(x=Technology, y= mean, fill = gender))+
  geom_bar(stat="identity", position=position_dodge())+
  #geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=0.2, position=position_dodge(0.9)) +
  ylim(0,5)+
  scale_fill_manual(values=c("red", "blue"), name="legend")+
  labs(y = "Mean perceived risk", x = "Energy Technologies")+
  ggtitle("Perceived risk and benefit from individually owned energy technologies by gender")+
  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))

library(gridExtra)
grid.arrange(p1, p2, ncol = 2)

@@

# conducting 
library(stats)

male_risk <- demovars[demovars$gender == "Male",]$Risky_Nuclear
female_risk <- demovars[demovars$gender == "Female",]$Risky_Nuclear

@@

library(dplyr)
library(purrr)

demovars %>% 
  filter(gender %in% c("Male", "Female"))%>%
  select(starts_with("Risky")) %>% 
  lapply(function(col) wilcox.test(col ~ gender, data = demovars))

@@

>>>>

@@

@@

p1 <- sum_gender%>% 
  filter(Technology %in% c("Wind","Nuclear","Solar","Oil","Hydro","Gas","Coal")) %>%
  ggplot(aes(x=Technology, y= median, fill = gender))+
  geom_bar(stat="identity", position=position_dodge())+
  #geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=0.2, position=position_dodge(0.9)) +
  ylim(0,5)+
  scale_fill_manual(values=c("red", "blue"), name="legend")+
  labs(y = "Median perceivd risk", x = "Energy Technologies")+
  ggtitle("Perceived risk and benefit from centrally owned energy technologies by gender")+
  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))+
  annotate("text", x=c("Solar", "Nuclear", "Coal"), y=4.8, label="*", size=10, fontface="bold") +
  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5, size=12, margin=margin(l=50)))

p2 <- sum_gender%>% 
  filter(Technology %in% c("INDHydro", "INDSolar", "INDWind", "INDBiogas","INDDiesel", "INDKerosene","INDFirewoodetc","INDLPG")) %>%
  ggplot(aes(x=Technology, y= median, fill = gender))+
  geom_bar(stat="identity", position=position_dodge())+
  #geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=0.2, position=position_dodge(0.9)) +
  ylim(0,5)+
  scale_fill_manual(values=c("red", "blue"), name="legend")+
  labs(y = "Median perceived risk", x = "Energy Technologies")+
  ggtitle("Perceived risk and benefit from individually owned energy technologies by gender")+
  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5)) +
  annotate("text", x=c("INDSolar", "INDBiogas", "INDDiesel"), y=4.8, label="*", size=10, fontface="bold") +
  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5, size=12, margin=margin(l=50)))

library(gridExtra)
grid.arrange(p1, p2, ncol = 2, widths = NULL)

@@

# conducting non-parametric procedure : "Wilcoxon rank-sum test" to see how perception of risk may differ according to gender.

library(broom)
library(stats)
library(dplyr)

male_risk<- demovars[demovars$gender == "Male",]$Risky_Nuclear 
female_risk <- demovars[demovars$gender == "Female",]$Risky_Nuclear

@@

Cmale_risk<- demovars[demovars$gender == "Male",]$Risky_Coal 
Cfemale_risk <- demovars[demovars$gender == "Female",]$Risky_Coal

wilcox.test(Cmale_risk, Cfemale_risk, alternative = "two.sided")

demovars_mf <- demovars %>% 
  filter(gender %in% c("Male", "Female"))

wilcox_gender <- demovars_mf %>%
  select(starts_with("Risky")) %>%
  lapply(function(col) wilcox.test(col ~ gender, data = demovars_mf))

wilcox_mf <- do.call(rbind, wilcox_gender)

# results from this are used to mark significant differences in the bar graph above.

@@

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)

demovars_caste_long <- demovars_caste %>%
  pivot_longer(cols = starts_with("Risky_"), names_to = "technology", values_to = "perceived_risk") %>%
  mutate(technology = gsub("Risky_", "", technology)) %>%
        mutate(caste = ifelse(grepl("SC|Scheduled caste", caste), "SC", caste),
              caste = ifelse(grepl("ST|Scheduled Tribe", caste), "ST", caste),
              caste = ifelse(grepl("OBC|Other Backward Classes", caste), "OBC", caste))

library(ggplot2)

# Subset dataframe with IND prefix
demovars_caste_long_ind <- demovars_caste_long %>% 
  filter(str_starts(technology, "IND"))%>%
   group_by(caste, technology) %>% 
  summarize(median_perceived_risk = median(perceived_risk))

table(demovars_caste_long_ind)

# Create bar graph with IND prefix 
ggplot(demovars_caste_long_ind, aes(x = technology, y = median_perceived_risk, fill = caste)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Median Perceived Risk by Caste Groups for Technologies with IND Prefix",
       x = "Technology", y = "Median Perceived Risk") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) # Rotate x-axis labels

# Subset dataframe without IND prefix
demovars_caste_long_not_ind <- demovars_caste_long %>% 
  filter(!str_starts(technology, "IND"))%>%
   group_by(caste, technology) %>% 
  summarize(median_perceived_risk = median(perceived_risk))

# Create bar graph without IND prefix

ggplot(demovars_caste_long_not_ind, aes(x = technology, y = median_perceived_risk, fill = caste)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Median Perceived Risk by Caste Groups for Technologies without IND Prefix",
       x = "Technology", y = "Median Perceived Risk") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) # Rotate x-axis labels

```
```{r}

# print the head of the file
head(demovars_caste_long)

# Show the group/caste levels

demovars_caste_long$caste <- factor(demovars_caste_long$caste)
levels(demovars_caste_long$caste)

# compute summary statistic by groups 
library(dplyr)
summary_caste <- group_by(demovars_caste_long, caste) %>%
  summarise(
    count = n(),
    mean = mean(perceived_risk, na.rm = TRUE),
    sd = sd(perceived_risk, na.rm = TRUE),
    median = median(perceived_risk, na.rm = TRUE),
    IQR = IQR(perceived_risk, na.rm = TRUE)
  )

summary(summary_caste)

library(ggplot2)

# Create the box plot with median values

demovars_caste_long$technology <- factor(demovars_caste_long$technology)
levels(demovars_caste_long$technology)

kruskal.test(perceived_risk ~ caste, data = demovars_caste_long)

pairwise.wilcox.test(demovars_caste_long$perceived_risk, demovars_caste_long$caste,
                 p.adjust.method = "BH")

library(dplyr)
#for Nuclear
Nuclear_caste <- demovars_caste_long %>%
  filter(technology == "Nuclear")

pairwise.wilcox.test(Nuclear_caste$perceived_risk, Nuclear_caste$caste,
                 p.adjust.method = "BH")

# For Coal
Coal_caste <- demovars_caste_long %>%
  filter(technology == "Coal")
pairwise.wilcox.test(Coal_caste$perceived_risk, Coal_caste$caste, p.adjust.method = "BH")

# For Gas
Gas_caste <- demovars_caste_long %>%
  filter(technology == "Gas")
pairwise.wilcox.test(Gas_caste$perceived_risk, Gas_caste$caste, p.adjust.method = "BH")

# For Hydro
Hydro_caste <- demovars_caste_long %>%
  filter(technology == "Hydro")
pairwise.wilcox.test(Hydro_caste$perceived_risk, Hydro_caste$caste, p.adjust.method = "BH")

# For INDBiogas
INDBiogas_caste <- demovars_caste_long %>%
  filter(technology == "INDBiogas")
pairwise.wilcox.test(INDBiogas_caste$perceived_risk, INDBiogas_caste$caste, p.adjust.method = "BH")

# For INDDiesel
INDDiesel_caste <- demovars_caste_long %>%
  filter(technology == "INDDiesel")
pairwise.wilcox.test(INDDiesel_caste$perceived_risk, INDDiesel_caste$caste, p.adjust.method = "BH")

# For INDFirewoodetc
INDFirewoodetc_caste <- demovars_caste_long %>%
  filter(technology == "INDFirewoodetc")
pairwise.wilcox.test(INDFirewoodetc_caste$perceived_risk, INDFirewoodetc_caste$caste, p.adjust.method = "BH")

# For INDHydro
INDHydro_caste <- demovars_caste_long %>%
  filter(technology == "INDHydro")
pairwise.wilcox.test(INDHydro_caste$perceived_risk, INDHydro_caste$caste, p.adjust.method = "BH")

# For INDKerosene
INDKerosene_caste <- demovars_caste_long %>%
  filter(technology == "INDKerosene")
pairwise.wilcox.test(INDKerosene_caste$perceived_risk, INDKerosene_caste$caste, p.adjust.method = "BH")

# For INDLPG
INDLPG_caste <- demovars_caste_long %>%
  filter(technology == "INDLPG")
pairwise.wilcox.test(INDLPG_caste$perceived_risk, INDLPG_caste$caste, p.adjust.method = "BH")

# For INDSolar
INDSolar_caste <- demovars_caste_long %>%
  filter(technology == "INDSolar")
pairwise.wilcox.test(INDSolar_caste$perceived_risk, INDSolar_caste$caste, p.adjust.method = "BH")

# For INDWind
INDWind_caste <- demovars_caste_long %>%
  filter(technology == "INDWind")
pairwise.wilcox.test(INDWind_caste$perceived_risk, INDWind_caste$caste, p.adjust.method = "BH")

# For Oil
Oil_caste <- demovars_caste_long %>%
  filter(technology == "Oil")
pairwise.wilcox.test(Oil_caste$perceived_risk, Oil_caste$caste, p.adjust.method = "BH")

# For Solar
Solar_caste <- demovars_caste_long %>%
  filter(technology == "Solar")
pairwise.wilcox.test(Solar_caste$perceived_risk, Solar_caste$caste, p.adjust.method = "BH")

# For Wind
Wind_caste <- demovars_caste_long %>%
  filter(technology == "Wind")
pairwise.wilcox.test(Wind_caste$perceived_risk, Wind_caste$caste, p.adjust.method = "BH")

#not finding any significant differences in the medians

```
```{r}

demovars_urban_rural <-  demovars %>%
  select(starts_with("Risky"), urban_rural) %>%
  pivot_longer(cols = starts_with("Risky_"), names_to = "technology", values_to = "perceived_risk") %>%
  mutate(technology = gsub("Risky_", "", technology)) %>%
  na.omit()

pairwise.wilcox.test(demovars_urban_rural$perceived_risk, demovars_urban_rural$urban_rural, p.adjust.method = "BH")
